An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-22 draft.tex
Controller section

\usepackage{lineno,hyperref}
\usepackage{rotating}
\usepackage{algpseudocode,algorithm}

@@

\subsection{Controller Container} 
\label{controller}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{marble_controller}
    \caption{Marble diagram for the Reactive Python implementation of the Controller}
    \label{fig:marble_controller}
\end{figure}

@@

\begin{algorithm}
    \caption{<your caption for this algorithm>}
    \label{<your label for references later in your document>}
    \begin{algorithmic}[1]
            \Procedure{Euclid}{$a,b$}\Comment{The g.c.d. of a and b}
            \State $r\gets a\bmod b$
            \While{$r\not=0$}\Comment{We have the answer if r is 0}
            \State $a\gets b$
            \State $b\gets r$
            \State $r\gets a\bmod b$
            \EndWhile\label{euclidendwhile}
            \State \textbf{return} $b$\Comment{The gcd is b}
            \EndProcedure

>>>>

\usepackage{lineno,hyperref}
\usepackage{rotating}
\usepackage{algpseudocode,algorithm}
\usepackage{hyperref}

@@

\subsection{Controller Container} 
\label{controller}

The controller is an essential component of the architecture (Figure \ref{fig:kafkEO})
because it is responsible for maintaining the evolutionary loop. It takes newly
evolved populations from the Output Queue, mixes them,   and produces new
messages from the result. At the same time, it must keep track of two conditions
for ending the loop: the number of messages it has received reaches a maximum
value, or the error of the best solution reaches a specific size.  Finally, it
must filter out remnant messages from other experients. Messages from other
experiments can remain in the queues because of the asynchronous nature of the
system.  We chose to implement the controller in Python but using an API
specialized in asynchronous event-driven programming over data streams.  The
open-source library is called Reactive Extensions for Python (RxPY)
\url{https://github.com/ReactiveX/RxPY} based on the Observer pattern
\cite{gamma1995design} and functional programming.

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{marble_controller}
    \caption{Marble diagram for the Reactive Python implementation of the Controller}
    \label{fig:marble_controller}
\end{figure}

@@

\begin{algorithm}
    \caption{Migration}
    \label{read}
    \begin{algorithmic}[1]
        \Procedure{cxBestFromEach}{$pop_1,pop_2$}
            \State $pop_1.sort()$
            \State $pop_2.sort()$
            \State $size\gets min(len(pop_1), len(pop_2))$
            \State $cxpoint\gets (size-1)/2$
            \State $pop_1[cxpoint:]\gets pop_2[:cxpoint+2]$
            \State \textbf{return} $pop_1$
        \EndProcedure
